Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks

### 2023-06-16 evaluation/evaluation.tex
Updates from Overleaf

Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$. This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding per window/time-frame, collecting and stacking these embeddings, and finally normalizing the resulting matrix or as we like to call it, \textit{embeddiogram}.

>>>>

Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$. This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using our pre-trained model to produce a vector per window/time-frame, collecting and stacking these embeddings, and finally normalizing the resulting matrix or as we like to call it, the \textit{embeddiogram}.
